---
title: "Chapter 5"
format:
  html:
    theme: cosmo
    toc: true
    number-sections: true
---

```{r}
require(tidymodels)
data(ames)
ames <- 
  ames |> 
  mutate(Sale_Price = log10(Sale_Price))

```

# Spending Our Data

-   **Training Set:** Sandbox for model building

-   **Test Set:** Only used **ONCE** as final arbiter between models to determine efficacy

```{r}
tidymodels_prefer()

theme_set(
  theme_minimal()
)
```

### Initial Split

```{r}
set.seed(501)

ames_split <- 
  initial_split(ames, prop = 0.8)

ames_split
```

### Obtain Training and Testing Data

```{r}
ames_train <- training(ames_split)
ames_test <- testing(ames_split)

dim(ames_train)
```

### Viz of Distribution of `Sale_Price`

```{r}
ggplot(
  ames,
  aes(x = Sale_Price)
  ) +
  geom_density() +
  geom_vline(
    data = tibble(
      x = quantile(ames$Sale_Price, probs = c(0.25, 0.5, 0.75))
    ),
    aes(
      xintercept = x
      ),
    linetype = 3
  )
```

### Using Stratified Sampling

```{r}
set.seed(502)
ames_split <- initial_split(ames, prop = 0.8, strata = Sale_Price)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```

### Information Leakage

***Information leakage occurs when data outside the training set are used in modeling process.***

## Code For Remainder of Book!

```{r}
#| eval: false
require(tidymodels)
data(ames)
ames <- 
  ames |> 
  mutate(
    Sale_Price = log10(Sale_Price)
  )

set.seed(502) 
ames_split <- initial_split(ames, prop = 0.8, strata = Sale_Price)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```
